Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-05-07 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Modified Kershaw closure section.

The basic principle behind Kershaw closure is derived from the fact that the realizable set defined by $(\cJ, \vect{\cH}, \vect{K})$ is convex.
Due to the convexity, it's sufficient and necessary for an element in the convex set be expressed as a convex combination of two elements that on the set boundary.
The Kershaw closure assumes that the convex combination has a constant coefficient which is independent from $(\cJ, \vect{\cH})$.
Therefore, using the lower occupancy limit, one can determine the coefficient and apply the convex combination as an approximation.
Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:
\begin{equation}
  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
\end{equation}

>>>>

The basic principle behind Kershaw closure is derived from the fact that the realizable set defined by $(\cJ, \vect{\cH}, \vect{K})$ is convex.
Due to the convexity, it's sufficient and necessary for an element in the convex set be expressed as a convex combination of two elements that on the set boundary.
The Kershaw closure assumes that the convex combination has a constant coefficient $\beta$ which is independent from $(\cJ,h)$:
\begin{align}
 \chi(\cJ,h) = \beta  \chi_{L}(\cJ,h) + (1-\beta) \chi_{U}(\cJ,h),
\end{align}
where $\chi_{L}$ and $\chi_{U}$ are the boundary functions given by the Heaviside function with Fermi-Dirac statistic function.
Therefore, using the lower occupancy limit,
\begin{align}
 \chi(\cJ,0) = \dfrac{1}{3},
\end{align}
one can determine the coefficient $\beta$ and apply the convex combination as an approximation.
Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:
\begin{equation}
  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
\end{equation}
